---
title: "STAT 331 Portfolio"
author: "Rachel Survilas"
format: html 
embed-resources: true
layout: margin-left
editor: visual
execute: 
  eval: false
  echo: true
---

[**My Grade:**]{.underline} I believe my grade equivalent to course work evidenced below to be an \_\_.

[**Learning Objective Evidence:**]{.underline} In the code chunks below, provide code from Lab or Challenge assignments where you believe you have demonstrated proficiency with the specified learning target. Be sure to specify **where** the code came from (e.g., Lab 4 Question 2).

## Working with Data

**WD-1: I can import data from a *variety* of formats (e.g., csv, xlsx, txt, etc.).**

-   `csv` Example 1

```{r}
#| label: wd-1-csv-1

#Lab 3

teacher_evals <- read_csv(here::here("Week 3", "Lab 3", "teacher_evals.csv"))

```

-   `csv` Example 2

```{r}
#| label: wd-1-csv-2

#Lab 4

childcare_costs <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-05-09/childcare_costs.csv')

counties <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-05-09/counties.csv')

tax_rev <- read_csv('https://atheobold.github.io/groupworthy-data-science/labs/instructions/data/ca_tax_revenue.csv')

```

-   `xlsx`

```{r}
#| label: wd-1-xlsx

#NA

```

**WD-2: I can select necessary columns from a dataset.**

-   Example selecting specified columns

```{r}
#| label: wd-2-ex-1

#Lab 3. This chunk satisfies the ability to select specified columns for this learning target.

teacher_evals_clean <- teacher_evals |> 
  rename(sex = gender) |> 
  filter(no_participants > 10) |> 
  mutate(
    across(
      .cols = c(teacher_id, course_id),
      .fns = ~ as.character(.x))
    )|> 
  select(
    course_id,
    teacher_id,
    question_no,
    no_participants,
    resp_share,
    SET_score_avg,
    percent_failed_cur,
    academic_degree,
    seniority,
    sex)

```

-   Example removing specified columns

```{r}
#| label: wd-2-ex-2


```

-   Example selecting columns based on logical values (e.g., `starts_with()`, `ends_with()`, `contains()`, `where()`)

```{r}
#| label: wd-2-ex-3

#Lab 4. In this code chunk I changed the column identifiers for pivot_longer so instead of selecting multiple columns using a colon I used the function starts_with.

ca_childcare |> 
  select(census_region,
         study_year,
         mc_infant, 
         mc_toddler,
         mc_preschool) |> 
  pivot_longer(cols = starts_with("mc_"),
               names_to = "Age",
               values_to = "Price") |> 
  mutate(Age = fct_recode(Age,
                              "Infant" = "mc_infant",
                              "Toddler" = "mc_toddler",
                              "Preschool" = "mc_preschool"),
       Age = fct_relevel(Age, 
                                "Infant",
                                "Toddler",
                                "Preschool")
       ) 

```

**WD-3: I can filter rows from a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   Numeric Example 1

```{r}
#| label: wd-3-numeric-ex-1

#Lab 3 Question 9. This code chunk shows that I can select specified columns and filter from the teacher_evals dataset for the amount of participants to be greater than 10.

teacher_evals_clean <- teacher_evals |> 
  rename(sex = gender) |> 
  filter(no_participants > 10) |> 
  mutate(
    across(
      .cols = c(teacher_id, course_id),
      .fns = ~ as.character(.x))
    )|> 
  select(
    course_id,
    teacher_id,
    question_no,
    no_participants,
    resp_share,
    SET_score_avg,
    percent_failed_cur,
    academic_degree,
    seniority,
    sex)

```

-   Numeric Example 2

```{r}
#| label: wd-3-numeric-ex-1

#Question 5 Lab 4. In this chunk I filtered the study year to only include the years 2008 and 2018.

ca_childcare |> 
  filter(study_year %in% c(2008, 2018)) |> 
  group_by(census_region, study_year) |>  
  summarise(median_household_income = median(mhi_2018, na.rm = TRUE),
            .groups = "drop") |>
  pivot_wider(names_from = study_year,
              values_from = median_household_income) |>
  arrange(desc(`2018`))

```

-   Character Example 1 (any context)

```{r}
#| label: wd-3-character

#Lab 5

inner_join(
  x = DL_person,
  y = get_fit_now_member,
  by = "name"
) |> 
  filter(membership_status == "gold",
         str_detect(plate_number,
                    pattern = "H42W"))

```

-   Character Example 2 (example must use functions from **stringr**)

```{r}
#| label: wd-3-string

#Lab 5. I used the str_detect function to identify the plate number of the suspect by the first 4 characters.

inner_join(
  x = DL_person,
  y = get_fit_now_member,
  by = "name"
) |> 
  filter(membership_status == "gold",
         str_detect(plate_number,
                    pattern = "H42W"))

```

-   Date (example must use functions from **lubridate**)

```{r}
#| label: wd-3-date



```

**WD-4: I can modify existing variables and create new variables in a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   Numeric Example 1

```{r}
#| label: wd-4-numeric-ex-1

#Lab 3. In this code chunk I 

teacher_evals_clean |> 
  group_by(
    teacher_id,
    course_id
  ) |> 
  summarize(
    distinct_questions_asked = n_distinct(question_no)
    ) |>
  filter(
    distinct_questions_asked == 9
    ) |> 
  kable()

```

-   Numeric Example 2

```{r}
#| label: wd-4-numeric-ex-2



```

-   Factor Example 1 (renaming levels)

```{r}
#| label: wd-4-factor-ex-1

#Lab 4. Gorwing: I am specifically looking for a tool that does the reordering of the legend for you since doing the reordering by hand is not a robust programming practice!


ca_childcare |> 
  select(census_region,
         study_year,
         mc_infant, 
         mc_toddler,
         mc_preschool) |> 
  pivot_longer(cols = mc_infant : mc_preschool,
               names_to = "Age",
               values_to = "Price") |> 
  mutate(Age = fct_recode(Age,
                              "Infant" = "mc_infant",
                              "Toddler" = "mc_toddler",
                              "Preschool" = "mc_preschool"),
       Age = fct_relevel(Age, 
                                "Infant",
                                "Toddler",
                                "Preschool")
       ) 

```

-   Factor Example 2 (reordering levels)

```{r}
#| label: wd-4-factor-ex-2

```

-   Character (example must use functions from **stringr**)

```{r}
#| label: wd-4-string

```

-   Date (example must use functions from **lubridate**)

```{r}
#| label: wd-4-date

```

**WD-5: I can use mutating joins to combine multiple dataframes.**

-   `left_join()` Example 1

```{r}
#| label: wd-5-left-ex-1

```

-   `right_join()` Example 1

```{r}
#| label: wd-5-right

```

-   `left_join()` **or** `right_join()` Example 2

```{r}
#| label: wd-5-left-right-ex-2

```

-   `inner_join()` Example 1

```{r}
#| label: wd-5-inner-ex-1

#Lab 5. In this section I used an inner_join to combine the DL_person dataset and get_fit_now_member dataset.

inner_join(
  x = DL_person,
  y = get_fit_now_member,
  by = "name"
) |> 
  filter(membership_status == "gold",
         str_detect(plate_number,
                    pattern = "H42W"))

```

-   `inner_join()` Example 2

```{r}
#| label: wd-5-inner-ex-2

```

**WD-6: I can use filtering joins to filter rows from a dataframe.**

-   `semi_join()`

```{r}
#| label: wd-6-semi

```

-   `anti_join()`

```{r}
#| label: wd-6-anti

```

**WD-7: I can pivot dataframes from long to wide and visa versa**

-   `pivot_longer()`

```{r}
#| label: wd-7-long

#Lab 4. In this code chunk I used pivot_longer to create two new columns: age of the child (Age) and price of childcare (Price).

ca_childcare |> 
  select(census_region,
         study_year,
         mc_infant, 
         mc_toddler,
         mc_preschool) |> 
  pivot_longer(cols = starts_with("mc_"),
               names_to = "Age",
               values_to = "Price") |> 
  mutate(Age = fct_recode(Age,
                              "Infant" = "mc_infant",
                              "Toddler" = "mc_toddler",
                              "Preschool" = "mc_preschool"),
       Age = fct_relevel(Age, 
                                "Infant",
                                "Toddler",
                                "Preschool")
       )

```

-   `pivot_wider()`

```{r}
#| label: wd-7-wide

#Question 5 Lab 4. In this chunk I used pivot_wider to create two new columns, 2008 and 2018, that has the median household income for each California region. 

ca_childcare |> 
  filter(study_year %in% c(2008, 2018)) |> 
  group_by(census_region, study_year) |>  
  summarise(median_household_income = median(mhi_2018, na.rm = TRUE),
            .groups = "drop") |>
  pivot_wider(names_from = study_year,
              values_from = median_household_income) |>
  arrange(desc(`2018`))

```

## Reproducibility

**R-1: I can create professional looking, reproducible analyses using RStudio projects, Quarto documents, and the here package.**

The following assignments satisfy the above criteria:

-   Example 1
-   Example 2
-   Example 3
-   Example 4
-   Example 5

**R-2: I can write well documented and tidy code.**

-   Example of **ggplot2** plotting

```{r}
#| label: r-2-1

#Challenge 4. In this code chunk I used ggplot to plot the median price for childcare type based on the proportion of Californians that identify as Hispanic.

ca_childcare |>
  mutate(hispanic = hispanic / 100) |>
  pivot_longer(cols = c("mfccsa", "mcsa"),
               names_to = "Childcare", 
               values_to = "Median_Price") |> 
  ggplot(aes(
    x = hispanic,
    y = Median_Price,
    color = Childcare)) +
  geom_smooth(lwd = 1.5) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 0.8)) +
  labs(
    x = "Percentage of population that identifies as Hispanic or Latino",
    y = "Median \n weekly \n price \n for \n childcare \n ($)",
    color = "Childcare type",
    title = "Family-based childcare versus center-based childcare for \n various hispanic proportions in California",
    subtitle = "Childcare type: <span style='color:#5D478B;'>center-based</span> and <span style='color:#6E8B3D;'>family-based</span> childcare"
  ) +
  theme_light() + 
  scale_color_manual(values = c("#5D478B", "#6E8B3D")) + 
  theme(
    plot.title = element_text(face = "bold", size = 15, hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.title.y = element_text(angle = 0, vjust = 0.5),
    plot.subtitle = ggtext::element_markdown(size = 13, hjust = 0.5),
    legend.position = ""
  )

```

-   Example of **dplyr** pipeline

```{r}
#| label: r-2-2

#Lab 3 Question 9. In this example I efficiently 

teacher_evals_clean |> 
  group_by(
    teacher_id,
    course_id
  ) |> 
  summarize(
    distinct_questions_asked = n_distinct(question_no)
    ) |>
  filter(
    distinct_questions_asked == 9
    ) |> 
  kable()

```

-   Example of function formatting

```{r}
#| label: r-2-3

```

**R-3: I can write robust programs that are resistant to changes in inputs.**

-   Example (any context)

```{r}
#| label: r-3-example

```

-   Example (function stops)

```{r}
#| label: r-3-function-stops

#NA 

```

## Data Visualization & Summarization

**DVS-1: I can create visualizations for a *variety* of variable types (e.g., numeric, character, factor, date)**

-   At least two numeric variables

```{r}
#| label: dvs-1-num

#Lab 4 Question 5. In this example I created a table (well-organized using the kable function) of the median household income for 2008 and 2018 for each of the ten California census regions. This code was changed from my original code. 

ca_childcare |> 
  filter(study_year %in% c(2008, 2018)) |> 
  group_by(census_region, study_year) |>  
  summarise(median_household_income = median(mhi_2018, na.rm = TRUE),
            .groups = "drop") |>
  pivot_wider(names_from = study_year,
              values_from = median_household_income,
              names_prefix = "Median_household_income_for_") |>
  arrange(desc(2018)) |> 
  kable()

```

-   At least one numeric variable and one categorical variable

```{r}
#| label: dvs-2-num-cat

#Lab 4 Question 5. This code is the same as above (modifications to my original code are still present) but since this table includes two numeric values as well as a categorical variable (California census regions) I included it in this learning target as well.

ca_childcare |> 
  filter(study_year %in% c(2008, 2018)) |> 
  group_by(census_region, study_year) |>  
  summarise(median_household_income = median(mhi_2018, na.rm = TRUE),
            .groups = "drop") |>
  pivot_wider(names_from = study_year,
              values_from = median_household_income,
              names_prefix = "Median_household_income_for_") |>
  arrange(desc(2018)) |> 
  kable()

```

-   At least two categorical variables

```{r}
#| label: dvs-2-cat

#Lab 3 Question 6. I am proud of this line of code as I was able to complete this data visualization in one pipeline using the across function. I also received kudos for how the syntax is on point! 

teacher_evals_clean |> 
  summarize(
    across(
      .cols = c(teacher_id, course_id),
      .fns = ~ n_distinct(.x))
    )

```

-   Dates (time series plot)

```{r}
#| label: dvs-2-date

#Lab 4 Question 7. In this code chunk, I created a plot of the median price for center-based childcare throughout the study years (2008 to 2018). I reordered the facets and legend, changed the plot colors, and size of the axes texts to match what Dr. T had.

ca_childcare |> 
  select(census_region,
         study_year,
         mc_infant, 
         mc_toddler,
         mc_preschool) |> 
  pivot_longer(cols = mc_infant : mc_preschool,
               names_to = "Age",
               values_to = "Price") |> 
  mutate(Age = fct_recode(Age,
                              "Infant" = "mc_infant",
                              "Toddler" = "mc_toddler",
                              "Preschool" = "mc_preschool"),
       Age = fct_relevel(Age, 
                                "Infant",
                                "Toddler",
                                "Preschool")
       ) |> 
  ggplot(aes(x = study_year,
             y = Price,
             color = fct_reorder2(.f = census_region,
                                  .x = study_year,
                                  .y = Price)
             ) 
           ) +
  geom_point() +
  facet_wrap(~ Age) + 
  labs(
    x = "Study Year",
    y = " ",
    color = "California Region",
    title = "Weekly Median Price for Center-Based Childcare ($)"
  ) +
  scale_color_discrete(
    name = "California Region"
  ) +
  geom_smooth(method = loess) + 
  scale_y_continuous(limits = c(100, 500),
                     breaks = seq(
                       from = 0, 
                       to = 500, 
                       by = 100)) +
  scale_x_continuous(limits = c(2008, 2018),
                     breaks = seq(
                       from = 2008,
                       to = 2018,
                       by = 2
                     )) +
  theme_bw() +
  theme(
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7),
    axis.text.y = element_text(size = 7),
    legend.text = element_text(size = 9),
    panel.spacing = unit(0.5, "lines") 
  ) + 
  scale_color_manual(values = plot_colors)

```

**DVS-2: I use plot modifications to make my visualization clear to the reader.**

-   I can modify my plot theme to be more readable

```{r}
#| label: dvs-2-ex-1

#Challenge 4.In this chunk I changed my original code to theme_light to produce a plot with light grey lines and axes to direct more attention towards the data.  

ca_childcare |>
  mutate(hispanic = hispanic / 100) |>
  pivot_longer(cols = c("mfccsa", "mcsa"),
               names_to = "Childcare", 
               values_to = "Median_Price") |> 
  ggplot(aes(
    x = hispanic,
    y = Median_Price,
    color = Childcare)) +
  geom_smooth(lwd = 1.5) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 0.8)) +
  labs(
    x = "Percentage of population that identifies as Hispanic or Latino",
    y = "Median \n weekly \n price \n for \n childcare \n ($)",
    color = "Childcare type",
    title = "Family-based childcare versus center-based childcare for \n various hispanic proportions in California",
    subtitle = "Childcare type: <span style='color:#5D478B;'>center-based</span> and <span style='color:#6E8B3D;'>family-based</span> childcare"
  ) +
  theme_light() + 
  scale_color_manual(values = c("#5D478B", "#6E8B3D")) + 
  theme(
    plot.title = element_text(face = "bold", size = 15, hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.title.y = element_text(angle = 0, vjust = 0.5),
    plot.subtitle = ggtext::element_markdown(size = 13, hjust = 0.5),
    legend.position = ""
  )

```

-   I can modify my colors to be accessible to anyone's eyes

```{r}
#| label: dvs-2-ex-2

#Challenge 4. I changed the code in this version so that my line colors would be seen by everyone, including color-blind folks!

ca_childcare |>
  mutate(hispanic = hispanic / 100) |>
  pivot_longer(cols = c("mfccsa", "mcsa"),
               names_to = "Childcare", 
               values_to = "Median_Price") |> 
  ggplot(aes(
    x = hispanic,
    y = Median_Price,
    color = Childcare)) +
  geom_smooth(lwd = 1.5) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 0.8)) +
  labs(
    x = "Percentage of population that identifies as Hispanic or Latino",
    y = "Median \n weekly \n price \n for \n childcare \n ($)",
    color = "Childcare type",
    title = "Family-based childcare versus center-based childcare for \n various hispanic proportions in California",
    subtitle = "Childcare type: <span style='color:#0072B2;'>center-based</span> and <span style='color:#D55E00;'>family-based</span> childcare"
  ) +
  theme_light() + 
  scale_color_manual(values = c("#0072B2", "#D55E00")) + 
  theme(
    plot.title = element_text(face = "bold", size = 15, hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.title.y = element_text(angle = 0, vjust = 0.5),
    plot.subtitle = ggtext::element_markdown(size = 13, hjust = 0.5),
    legend.position = ""
  )

```

-   I can modify my plot titles to clearly communicate the data context

```{r}
#| label: dvs-2-ex-3

#Challenge 4. In this challenge we were asked to create a plot answering a specific research question. My question was: Is there a difference between the full-time median price for childcare in a center-based setting and a family (in-home) setting in California for various Hispanic proportions? I made sure to include a plot title, axes titles, and a subtitle that clearly provided this context. 

ca_childcare |>
  mutate(hispanic = hispanic / 100) |>
  pivot_longer(cols = c("mfccsa", "mcsa"),
               names_to = "Childcare", 
               values_to = "Median_Price") |> 
  ggplot(aes(
    x = hispanic,
    y = Median_Price,
    color = Childcare)) +
  geom_smooth(lwd = 1.5) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 0.8)) +
  labs(
    x = "Percentage of population that identifies as Hispanic or Latino",
    y = "Median \n weekly \n price \n for \n childcare \n ($)",
    color = "Childcare type",
    title = "Family-based childcare versus center-based childcare for \n various hispanic proportions in California",
    subtitle = "Childcare type: <span style='color:#0072B2;'>center-based</span> and <span style='color:#D55E00;'>family-based</span> childcare"
  ) +
  theme_light() + 
  scale_color_manual(values = c("#0072B2", "#D55E00")) + 
  theme(
    plot.title = element_text(face = "bold", size = 15, hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.title.y = element_text(angle = 0, vjust = 0.5),
    plot.subtitle = ggtext::element_markdown(size = 13, hjust = 0.5),
    legend.position = ""
  )

```

-   I can modify the text in my plot to be more readable

```{r}
#| label: dvs-2-ex-4

#Challenge 4. For this ggplot code I increased the font size using element_text for the plot title, subtitle, and axes titles. I also changed the angle of the y-axis to horizontal and centered it so it would be easier to read.

ca_childcare |>
  mutate(hispanic = hispanic / 100) |>
  pivot_longer(cols = c("mfccsa", "mcsa"),
               names_to = "Childcare", 
               values_to = "Median_Price") |> 
  ggplot(aes(
    x = hispanic,
    y = Median_Price,
    color = Childcare)) +
  geom_smooth(lwd = 1.5) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 0.8)) +
  labs(
    x = "Percentage of population that identifies as Hispanic or Latino",
    y = "Median \n weekly \n price \n for \n childcare \n ($)",
    color = "Childcare type",
    title = "Family-based childcare versus center-based childcare for \n various hispanic proportions in California",
    subtitle = "Childcare type: <span style='color:#0072B2;'>center-based</span> and <span style='color:#D55E00;'>family-based</span> childcare"
  ) +
  theme_light() + 
  scale_color_manual(values = c("#0072B2", "#D55E00")) + 
  theme(
    plot.title = element_text(face = "bold", size = 15, hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.title.y = element_text(angle = 0, vjust = 0.5),
    plot.subtitle = ggtext::element_markdown(size = 13, hjust = 0.5),
    legend.position = ""
  )

```

-   I can reorder my legend to align with the colors in my plot

```{r}
#| label: dvs-2-ex-5

#Challenge 4. I modified the code to include a legend and modified the legend to include the specific hex colors used for each childcare type (family based and center based).

ca_childcare |>
  mutate(hispanic = hispanic / 100) |>
  pivot_longer(cols = c("mfccsa", "mcsa"),
               names_to = "Childcare", 
               values_to = "Median_Price") |> 
  ggplot(aes(
    x = hispanic,
    y = Median_Price,
    color = Childcare)) +
  geom_smooth(lwd = 1.5) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 0.8)) +
  labs(
    x = "Percentage of population that identifies as Hispanic or Latino",
    y = "Median \n weekly \n price \n for \n childcare \n ($)",
    color = "Childcare type",
    title = "Family-based childcare versus center-based childcare \n for various hispanic proportions in California",
    ) +
  theme_light() + 
  scale_color_manual(values = c("#5D478B", "#6E8B3D")) + 
  theme(
    plot.title = element_text(face = "bold", size = 15, hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.title.y = element_text(angle = 0, vjust = 0.5),
    plot.subtitle = ggtext::element_markdown(size = 13, hjust = 0.5),
    legend.position = "top"
  )

```

**DVS-3: I show creativity in my visualizations**

-   I can use non-standard colors (Example 1)

```{r}
#| label: dvs-3-1-ex-1

#Challenge 4. In this ggplot code I used a sage green (#6E8B3D) and purple (#5D478B) to identify the different childcare types. After seeing another student include these colors in his subtitle (which is a brilliant way to include the legend!) I did the same with these colors. 

ca_childcare |>
  mutate(hispanic = hispanic / 100) |>
  pivot_longer(cols = c("mfccsa", "mcsa"),
               names_to = "Childcare", 
               values_to = "Median_Price") |> 
  ggplot(aes(
    x = hispanic,
    y = Median_Price,
    color = Childcare)) +
  geom_smooth(lwd = 1.5) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 0.8)) +
  labs(
    x = "Percentage of population that identifies as Hispanic or Latino",
    y = "Median \n weekly \n price \n for \n childcare \n ($)",
    color = "Childcare type",
    title = "Family-based childcare versus center-based childcare for \n various hispanic proportions in California",
    subtitle = "Childcare type: <span style='color:#5D478B;'>center-based</span> and <span style='color:#6E8B3D;'>family-based</span> childcare"
  ) +
  theme_light() + 
  scale_color_manual(values = c("#5D478B", "#6E8B3D")) + 
  theme(
    plot.title = element_text(face = "bold", size = 15, hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.title.y = element_text(angle = 0, vjust = 0.5),
    plot.subtitle = ggtext::element_markdown(size = 13, hjust = 0.5),
    legend.position = ""
  )

```

-   I can use non-standard colors (Example 2)

```{r}
#| label: dvs-3-1-ex-2

```

-   I can use annotations (e.g., `geom_text()`)

```{r}
#| label: dvs-3-2

```

-   I can choose creative geometries (e.g., `geom_segment()`, `geom_ribbon)()`)

```{r}
#| label: dvs-3-3

```

**DVS-4: I can calculate numerical summaries of variables.**

-   Example using `summarize()`

```{r}
#| label: dvs-4-summarize

```

-   Example using `across()`

```{r}
#| label: dvs-4-across

#Lab 3 Question 6. Using the across function, I was able to find how many unique instructors and courses in the teacher_evals_clean dataset.  

teacher_evals_clean |> 
  summarize(
    across(
      .cols = c(teacher_id, course_id),
      .fns = ~ n_distinct(.x))
    )

```

**DVS-5: I can find summaries of variables across multiple groups.**

-   Example 1

```{r}
#| label: dvs-5-1

```

-   Example 2

```{r}
#| label: dvs-5-2

```

**DVS-6: I can create tables which make my summaries clear to the reader.**

-   I can modify my column names to clearly communicate the data context

```{r}
#| label: dvs-6-ex-1

```

-   I can modify the text in my table to be more readable (e.g., bold face for column headers)

```{r}
#| label: dvs-6-ex-2

```

-   I can arrange my table to have an intuitive ordering

```{r}
#| label: dvs-6-ex-3

```

**\*DVS-7: I show creativity in my tables.**

-   I can use non-default colors

```{r}
#| label: dvs-7-ex-1

#NA 

```

-   I can modify the layout of my table to be more readable (e.g., `pivot_longer()` or `pivot_wider()`)

```{r}
#| label: dvs-7-ex-2

#NA 

```

## Program Efficiency

**PE-1: I can write concise code which does not repeat itself.**

-   using a single function call with multiple inputs (rather than multiple function calls)

```{r}
#| label: pe-1-one-call



```

-   using `across()`

```{r}
#| label: pe-1-across

#Lab 3 Question 6. This code was awarded as exemplary for having concise and on-point syntax. 

teacher_evals_clean |> 
  summarize(
    across(
      .cols = c(teacher_id, course_id),
      .fns = ~ n_distinct(.x))
    )

```

-   using functions from the `map()` family

```{r}
#| label: pe-1-map-1

#NA 

```

**\*PE-2: I can write functions to reduce repetition in my code.**

-   Example 1: Function that operates on vectors

```{r}
#| label: pe-2-1

#NA

```

-   Example 2: Function that operates on data frames

```{r}
#| label: pe-2-2

#NA

```

-   Example 3: Function that operates on vectors *or* data frames

```{r}
#| label: pe-2-3

#NA

```

**PE-3:I can use iteration to reduce repetition in my code.**

-   using `across()`

```{r}
#| label: pe-3-across

```

-   using a `map()` function with **one** input (e.g., `map()`, `map_chr()`, `map_dbl()`, etc.)

```{r}
#| label: pe-3-map-1

#NA 

```

-   using a `map()` function with **more than one** input (e.g., `map_2()` or `pmap()`)

```{r}
#| label: pe-3-map-2

#NA

```

**PE-4: I can use modern tools when carrying out my analysis.**

-   I can use functions which are not superseded or deprecated

```{r}
#| label: pe-4-1

```

-   I can connect a data wrangling pipeline into a `ggplot()`

```{r}
#| label: pe-4-2

#Challenge 4. In this pipeline I created two new columns: Childcare (type of childcare parents used in California) and Median_Price (the median price for each childcare type), as well as changed the column showing proportion of people in California who are Hispanic (hispanic) so that I could add percentages to my x-axis. After this data wrangling I piped the dataset into ggplot to produce a plot showing the median price of childcare (family-based and center-based) based on the porportion of California residents who identify as Hispanic.  

ca_childcare |>
  mutate(hispanic = hispanic / 100) |>
  pivot_longer(cols = c("mfccsa", "mcsa"),
               names_to = "Childcare", 
               values_to = "Median_Price") |> 
  ggplot(aes(
    x = hispanic,
    y = Median_Price,
    color = Childcare)) +
  geom_smooth(lwd = 1.5) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 0.8)) +
  labs(
    x = "Percentage of population that identifies as Hispanic or Latino",
    y = "Median \n weekly \n price \n for \n childcare \n ($)",
    color = "Childcare type",
    title = "Family-based childcare versus center-based childcare for \n various hispanic proportions in California",
    subtitle = "Childcare type: <span style='color:#5D478B;'>center-based</span> and <span style='color:#6E8B3D;'>family-based</span> childcare"
  ) +
  theme_light() + 
  scale_color_manual(values = c("#5D478B", "#6E8B3D")) + 
  theme(
    plot.title = element_text(face = "bold", size = 15, hjust = 0.5),
    axis.title = element_text(size = 12),
    axis.title.y = element_text(angle = 0, vjust = 0.5),
    plot.subtitle = ggtext::element_markdown(size = 13, hjust = 0.5),
    legend.position = ""
  )

```

## Data Simulation & Statisical Models

**\*DSSM-1: I can simulate data from a *variety* of probability models.**

-   Example 1

```{r}
#| label: dsm-1-1

#NA

```

-   Example 2

```{r}
#| label: dsm-1-2

#NA 

```

**DSSM-2: I can conduct common statistical analyses in R.**

-   Example 1

```{r}
#| label: dsm-2-1

```

-   Example 2

```{r}
#| label: dsm-2-2

```

-   Example 3

```{r}
#| label: dsm-2-3

```

## Revising My Thinking

<!-- How did you revise your thinking throughout the course? How did you revise your thinking on the code examples you have provided in your portfolio? -->

<!-- For the revisions included in your Portfolio, to help me understand the nature of your revisions, please denote somehow the feedback I provided you (e.g., boldface, italics, colored text) before your revisions. -->

## Extending My Thinking

<!-- How did you extended your thinking throughout the course? How did you extend your thinking on the code examples you have provided in your portfolio? -->

## Peer Support & Collaboration

<!-- Include an image or a description of feedback you gave that you are proud of (either in a peer review or in Discord). -->

<!-- Include a description of how you grew as a collaborator through the weekly pair programming activities.   -->
